Microtransaction is the Future of MMORPGs

### 2022-05-09 outputs/paper/paper.Rmd
"Corrected several grammatical mistakes in the paper."

---
title: "Microtransaction is the Future of MMORPGs"
author: 
  - Tian Yi Zhang
thanks: "Code and data are available at: https://github.com/zhan7818/bdo_monetization"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "Advertisement and monetization schemes are essential to obtaining a stable revenue stream and ensuring the continued surival of an online video game. We obtain data through a survey distributed in several online communities for the massively multiplayer online game known as Black Desert Online and analyze it throuhg several graphs, tables, and a model in this paper. Results show a positive correlation between players' total playtimes, rated importance of subscription items, and their total monetary spending in the in-game cash shop. Players with a female main character in the game spend on average 9.23% more real world currency on cosmetic items in-game. On average, upfront cost for the game accounts for only 5-6% of a player's total spending on the game. These findings suggest that MMORPGs should release with an upfront cost before transitioning to free-to-play later down the line. The introduction of more than one type of subscription items becomes marginally less profitable. Further analysis on the topic of whales is recommended. Keywords: VP, BK, OM, Whale, MMORPG, Subscription, Pearl Shop, Central Market, Black Desert Online, Gender, Microtransaction"
output:
  bookdown::pdf_document2
toc: TRUE
bibliography: references.bib
---

@@

Up until a decade or two ago, singleplayer-driven content was the predominant
focus in the video game industry. This was mostly a product of the time, as the
infrastructures needed to support online-based video games were yet to be
fully developed. More importantly, what this also meant was a lack of 
post-launch updates being delivered for a game, as developers also lacked means
to deliver constant updates effectively into the hands of the consumers. As a
result, most video games received little to no post-launch updates aside from
one or two major expansions to their games that contained sufficient content
to be put on the shelves as add-ons to the original purchase.
Despite this, consumers back then were generally content with the amount of 
content they received for their purchases.

@@

The most prominent examples of live service online video games are the massively
multiplayer online role-playing games (MMORPG), a genre of video games known
specifically for its focus on multiplayer. Due to their focus on 
progression-based gameplay, developers of MMORPGs must constantly create new
and refreshing content to add to their games. To subsidize the development
costs that go along with it, developers have created a variety of monetization
models to ensure a steady revenue stream. For example, World of Warcraft, one
of the biggest MMORPGs, relies primarily on a monthly subscription from its
players. Others, such as Lost Ark, adopt a mix of strategies with 
a monthly subscription that grants
massive boosts in-game and an in-game cash shop that allows players to
purchases items for a variety of purposes using real world currencies.
If done properly, an analysis
on the monetization schemes of MMORPGs could have meaningful
implications for future MMORPG developers on how they should monetize their
video games to maximize revenue.

This paper primarily focuses on the MMORPG known as Black Desert Online,
commonly and henceforth referred to as BDO.
as it is MMORPG that utilizes a of mix of upfront cost, subscription and in-game
cash shop. Pearl Abyss, the developers behind Black Desert Online, 
never published any official statistics that touch upon the revenue of
Black Desert Online. As such, the following analysis will rely on data 
collected by the author of this paper.

@@

Due to the lack of APIs provided by Pearl Abyss that concerns the subject of
this paper, convenience sampling is used to collect data from the general
playerbase for the game. The survey is created in Google Forms and is
distributed to Black Desert Online players on Steam discussion, Black Desert
Online forum board, and the Black Desert Online subreddit on Reddit.^[A PDF
copy of the survey can be found in the github repo for this paper in 
inputs/survey/bdo_survey.pdf.]
The survey
consists of questions mostly regarding the respondents' amount of spending in
the various monetization models employed by Black Desert Online, as well as
some general background information regarding each respondent and their in-game
characters. The survey questions could be largely divided into the following set
of topics:

@@

In the post containing the survey on each of the distributed sites mentioned 
above, efforts were made to be
as transparent as possible with the participants: respondents were 
informed of the intended usage for the data collected and were assured that
no information that can be used to identify them will be collected nor
included in the survey and final paper.

@@

A total of 212 responses were collected from the survey. The data was exported
to excel [@citeExcel] where the columns names were shortened to be readable.
Two new columns were created from the responses:
* packages_usd: amount in USD spent on purchasing game packages
* packages_free: binary indicator of whether the respondent received the game
for free

@@

There are two methods to purchase premium items in this game: through the
`central market` or through the `pearl shop`. Pearl shop is BDO's cash shop,
accessible to every player, where players could use `pearls`, a currency
converted from real world currencies, to purchase premium items for cosmetic
and functional purposes. Furthermore, players who purchased premium items in
the pearl shop could list these items onto the central market for sale. Other
players could then use `silver`, the primary in-game currency, to purchase
the said premium items. This system serves as a way for some players to obtain
more silver using real world currencies, and for other players to obtain
premium items without ever spending any real world currencies to do so.

@@

Figure \@ref(fig:graph9) plots the rated importance of VP, and BK and OM.
We can observe that there is a considerable number of respondents who consider
VP as extremely critical to their enjoyment of the game. At the same time,
we can see a large number of
respondents consider BK and OM largely unimportant to their enjoyment of the
game. This shows that subscription-esque items are not universally regarded
as equally valuable by the respondents.

@@

An important aspect of the central market in BDO is the issue of supply and demand:
Despite being able to list most cosmetic items onto the central market,
there is generally always more demand for these cosmetic items than the supply.
To combat the issue of price inflation, most items that can be listed on the
central market in BDO--including value packs--have a price ceiling as
dictated by the developers of the game. When that price ceiling is reached
(i.e., the highest pre-order price placed for the item is the maximum price point),
any further listings of the item will instead `randomly` choose a player with a
max-priced pre-order placed and sell the item to the said player.

Because of the mechanic described above, an item pre-ordered at its price ceiling
does not follow a first-come first-serve basis and the central market instead relies
on randomness to decide which player to sell the item to. This means for items
with drastically higher demand than supply (such as a value pack), players
are never guaranteed to obtain the item, regardless of how long they have
placed the pre-order for the said item already. This often leads to cases
where a player could place a pre-order for an item for an extensive period of 
time (months or years) yet never successfully purchases the item from the
central market.

Figure \@ref(fig:graph1) showcases this issue: For respondents who claimed
that having a VP active is crucial to their enjoyment of the game, only a few
reported having consistent success purchasing VPs from the central market.
Because of this, respondents could be pressured into relying more 
on purchasing VPs through the pearl shop.

@@

Gender-based appeal is a deep-rooted design pattern in most Korean MMOs.
(`FIND SOME SOURCE FOR THIS SHIT`)
Most cosmetic options are designed to appeal to the general playerbase and often
forfeits any semblance of practicality. This issue is very apparent in female
armor designs in Korean MMOs, and Black Desert Online is generally not an
exception to this. 
There are 13 adult female characters in BDO and 9 adult male characters.
To see if these appeal-based design decisions truly have
any merit behind them, data was collected on the number of adult
female characters that each respondent has. The intent is to compare it with
their spending in cosmetic items, as briefly demonstrated in
Figure \@ref(fig:graph4).

@@

The general assumption behind the consideration of this model is that
as a player spends more time in BDO, the more likely they are to spend more
real world currencies in exchange for in-game items. This could be due to their
need to continue using subscription-esque items that grant them boosts, or
due to the creation of more content in the game that requires real world
currencies to purchase (such as cosmetic items). Given the context of 
gender-based appeal in Korean MMOs such as BDO, there could also be a connection
between number of female characters and a player's spending in the pearl shop.
The model therefore seeks to explore whether there 
really is a statistically significant connection between the total amount
of money spent in-game and the factors mentioned above. 
Equivalently,

@@

Equation \@ref(eq:linm) represents the model used in this paper, where
$Y$, the dependent variable, is a player's total spending in pearl shop,
$\beta_0$ is the intercept, $X_1$ is the covariate of total playtime,
$X_2$ is the covariate of number of female characters the player has.
$X_3$ is the covariate of the player's rated importance of VP.
$X_4$ is the covariate of the player's rated importance of BK and OM.
$\beta_1 \beta_2, \beta_3, \beta_4$ are the coefficients of the variables.

@@

The Normal Q-Q plot (top-right) shows most points falling on the dashed line,
though there are also a considerable number of points that fall off the dashed line
on the right tail end, suggesting that the residuals may not be entirely normally
distributed.

@@

As shown in Table \@ref(tab:table1), some of the respondents had obtained the
free package for the game, which were frequently given out through various
methods by the developer and publisher of BDO, as described in Section
\@ref(preliminary-analysis). Out of the 67 respondents
who obtained the free package of the game, 23 of them remained completely
free-to-play and did not spend any real world currency to purchase in-game
items nor other game packages.
The other 44 respondents--almost double those who remained completely
free-to-play--either purchased in-game items on the pearl shop or other game
packages.

This is further elaborated upon in Table \@ref(tab:table3), which summarises
the dataset based on whether the respondent's spending status is considered
`completely free` if they obtained the free package for the game and did not
spent money on other game packages nor in the pearl shop, and `partially free`
if they obtained the free package for the game but spent money on other
game packges and/or in the pearl shop.
We can see from Table \@ref(tab:table3) that despite having a lower average
spending in both the pearl shop and game packages, the "partially free" players
still spent a substantial amount of money on further purchases for the game:
On average, for "partially free" respondents,
the amount of money spent on game package purchases accounts for only 6% of
their total spending on BDO. We observe a similar statistic for players who
did not obtain a free package for the game, whose spending on game packages
accounts for only 5% of their total spending on BDO.
In contrast, microtransactions in BDO accounts for roughly 95% of the total
revenue, as show in table \@ref(tab:table4), a staggeringly high difference.

@@

As discussed in \@ref(preliminary-analysis), Figure \@ref(fig:graph9) suggests
a difference in importance as regarded by the respondents. This is supported
by the statistics shown in Figure \@ref(fig:graph8), which show a stronger
positive linear correlation between rated importance of VP and spending on
VP when compared to the correlation between rated importance of BK and OM and
spending on BK and OM. On average, respondents spend $148.0288 USD on
purchasing VP from the pearl shop, and spend $49.1202 USD on purchasing
BK and OM from the pearl shop.

Table \@ref(tab:table3) shows that on average, VP accounts for 11% of
a respondent's total spending on BDO (15% for partially free respondents).
BK and OM accounts for 4% of a respondent's total spending on BDO (5% for
partially free respondents).

@@

From a pure-revenue standpoint, there is a debate to be made about whether
or not a video game publisher
should charge an upfront cost on consumers for access to their game.
On one hand, giving concrete price tags to a game before its launch would grant
the publisher the strategy to let consumers pre-order the game, injecting a
massive amount of funding into the company that could be used for future
developments and investments on other projects well before they even need to
finish and release the game.
On the other hand, price tags too high may discourage consumer interest in the
game, preventing them from ever engaging with the in-game cash shop which
is much better suited for long-term revenue generation.

@@

Another potential reason to this disinterest is the difference in price between
BK and OM, and VP: Without any discounts, 30 days of VP costs 1500 pearls
(roughly \$15.00 USD) while 30 days of BK/OM costs 2500 pearls (roughly \$25.00
USD), an increase in price by roughly 66%. There is no plausible explanation
as to why BK/OM are priced higher than VP except publisher bias; While most
players regard VP as the more important subscription item (as shown in Figure
\@ref(fig:graph9)), publishers of the game may simply think otherwise.
If possible, further extensions on this study should inquire the players about
their reasons for rating certain subscription items less important, be it the
price of its bonuses.

@@

Whales are often make up a major portion of a video game's revenue:
For example, according to Activision Blizzard's [@citeacti] 2021 fourth quarter
revenue release,
the company made a net revenue of \$8.086 billion USD, \$5.736 billion USD of
which is from in-game transactions and subscriptions. A surprising high 70.94%
of total revenue for the company is from sources other than upfront costs.

@@

As Table \@ref(tab:table4) shows, if we do not exclude the whales as outliers
from the dataset, then the average
revenue generated from the pearl shop accounts for roughly 95% 
This clearly demonstrates the importance of whales to a video game company's
profit, and why catering to these whales could often result in more profit
than focusing on satisfying to the average consumer.

Whales are rare but their impact have not gone unnoticed. In fact, catering to 
whales is not a new
strategy for publishers by any means, as demonstrated by Jernström [@citepocket] 
, who is well versed in this type of monetisation and
has created a thorough guide for other publishers to follow suit. It is apparent
that publishers are already catching on to these whales and the best strategy
to appeal to them. This should state the significance of whales as the highest
potential source of income for a video game.

>>>>

---
title: "Microtransaction is the Future of MMORPGs"
author: 
  - Tian Yi Zhang
thanks: "Code and data are available at: https://github.com/zhan7818/bdo_monetization"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "Advertisement and monetization schemes are essential to obtaining a stable revenue stream and ensuring the continued surival of an online video game. We obtain data through a survey distributed in several online communities for the massively multiplayer online game known as Black Desert Online developed by Pearl Abyss and analyze it through several graphs, tables, and a model in this paper. Results show a positive correlation between a player's total playtime, rated importance of subscription items, and their total monetary spending in the in-game cash shop. Players with a female main character in the game spend on average 9.23% more real world currency on cosmetic items in-game. On average, upfront cost for the game accounts for only 5-6% of a player's total spending on the game. These findings suggest that MMORPGs should release with an upfront cost before transitioning to free-to-play later down the line. The introduction of more than one type of subscription items becomes marginally less profitable. Further analysis on the topic of whales is recommended. Keywords: VP, BK, OM, Whale, MMORPG, Subscription, Pearl Shop, Central Market, Black Desert Online, Pearl Abyss, Gender, Microtransaction"
output:
  bookdown::pdf_document2
toc: TRUE
bibliography: references.bib
---

@@

Up until a decade or two ago, singleplayer-driven content was the predominant
focus in the video game industry. This was mostly a product of the time, as the
infrastructures needed to support online-based video games were yet to be
fully developed. More importantly, what this also meant was a lack of 
post-launch updates being delivered for a game, as developers also lacked means
to deliver constant updates effectively into the hands of the consumers. As a
result, most video games received little to no post-launch updates aside from
one or two major expansions that contained sufficient content
to be put on the shelves as add-ons to the original product.
Despite this, consumers back then were generally content with the amount of 
content they received for their purchases.

@@

The most prominent examples of live service online video games are the massively
multiplayer online role-playing games, henceforth referred to as
MMORPG, a genre of video games known
specifically for its focus on multiplayer. Due to their focus on 
progression-based gameplay, developers of MMORPGs must constantly create new
and refreshing content to add to their games. To subsidize the development
costs that go along with it, developers have created a variety of monetization
models to ensure a steady revenue stream. For example, World of Warcraft, one
of the biggest MMORPGs, relies primarily on a monthly subscription from its
players. Others, such as Lost Ark, adopt a mix of strategies with 
a monthly subscription that grants
massive boosts in-game and an in-game cash shop that allows players to
purchases items for a variety of purposes using real world currencies.
If done properly, an analysis
on the monetization schemes of MMORPGs could have meaningful
implications for future MMORPG developers on how they should monetize their
video games to maximize revenue.

This paper primarily focuses on the MMORPG known as `Black Desert Online`,
commonly and henceforth referred to as BDO,
as it is an MMORPG that utilizes a of mix of upfront cost
, subscription and in-game
cash shop. `Pearl Abyss`, the developers behind Black Desert Online, 
never published any official statistics that touch upon the revenue of
Black Desert Online. As such, the following analysis will rely on data 
collected by the author of this paper.

@@

Due to the lack of APIs provided by Pearl Abyss that concerns the subject of
this paper, convenience sampling is used to collect data from the general
North American and European
playerbase for the game. The survey is created in Google Forms and is
distributed to Black Desert Online players on Steam discussion, Black Desert
Online forum board, and the Black Desert Online subreddit on Reddit.^[A PDF
copy of the survey can be found in the github repo for this paper in 
inputs/survey/bdo_survey.pdf.]
The survey
consists of questions mostly regarding the respondents' amount of spending in
the various monetization models employed by Black Desert Online, as well as
some general background information regarding each respondent and their in-game
characters. The survey questions could be largely divided into the following set
of topics:

@@

In the post containing the survey on each of the distributed sites mentioned 
above, efforts were made to be
as transparent as possible with the participants: respondents were 
informed of the intended usage for the data collected and were assured that
no information that can be used to identify them will be collected nor
included in the survey and the final paper.

@@

A total of 212 responses were collected from the survey. The data was exported
to Excel [@citeExcel] where the columns names were shortened to be readable.
Two new columns were created from the responses:

* packages_usd: amount in USD spent on purchasing game packages
* packages_free: binary indicator of whether the respondent received the game
for free

@@

There are two methods to purchase premium items in this game, through the
`central market` or through the `pearl shop`: The pearl shop is BDO's cash shop,
accessible to every player, where players could use `pearls`, a currency
converted from real world currencies, to purchase premium items for cosmetic
and functional purposes. Furthermore, players who purchased premium items in
the pearl shop could list these items onto the central market for sale. Other
players could then use `silver`, the primary in-game currency, to purchase
the said premium items. This system serves as a way for some players to obtain
more silver using real world currencies, and for other players to obtain
premium items without ever spending any real world currencies to do so.

@@

Figure \@ref(fig:graph9) plots the rated importance of VP, and BK and OM.
We can observe that there is a considerable number of respondents who consider
VP as extremely critical to their enjoyment of the game. At the same time,
we can see that a large number of
respondents consider BK and OM largely unimportant to their enjoyment of the
game. This shows that subscription-esque items are not universally regarded
as equally valuable by the respondents.

@@

An important aspect of the central market in BDO is the issue of supply and demand:
Despite being able to list most cosmetic items onto the central market,
there is generally always more demand for these cosmetic items than supply.
To combat the issue of price inflation, most items that can be listed on the
central market in BDO--including value packs--have a price ceiling as
dictated by the developers of the game. When that price ceiling is reached
(i.e., the highest pre-order price placed for the item is the maximum price point),
any further listings of the item will instead `randomly` choose a player with a
max-priced pre-order placed and sell the item to the said player.

Because of the mechanic described above, an item pre-ordered at its price ceiling
does not follow a first-come first-serve basis and the central market instead relies
on randomness to decide which player to sell the item to. This means that 
for items
with drastically higher demand than supply (such as a value pack), players
are never guaranteed to obtain the item, regardless of how long they have
placed the pre-order for the said item already. This often leads to cases
where a player could place a pre-order for an item for an extensive period of 
time (months or years) yet never successfully purchases the item from the
central market.

Figure \@ref(fig:graph2) showcases this issue: For respondents who claimed
that having a VP active is crucial to their enjoyment of the game, only a few
reported having consistent success purchasing VPs from the central market.
Because of this, respondents could be pressured into relying more 
on purchasing VPs through the pearl shop.

@@

Gender-based appeal is a deep-rooted design pattern in most Korean MMOs.
Most cosmetic options are designed to appeal to the general playerbase and often
forfeits any semblance of practicality. This issue is very apparent in female
armor designs in Korean MMOs, and Black Desert Online is generally not an
exception to this. 
There are 13 adult female characters in BDO and 9 adult male characters.
To see if these appeal-based design decisions truly have
any merit behind them, data was collected on the number of adult
female characters that each respondent has. The intent is to compare it with
their spending in cosmetic items, as briefly demonstrated in
Figure \@ref(fig:graph4).

@@

The general assumption behind the consideration of this model is that
as a player spends more time in BDO, the more likely they are to spend more
real world currencies in exchange for in-game items. This could be due to their
need to continue using subscription-esque items that grant them boosts, or
due to the creation of more content in the game that requires real world
currencies to purchase (such as cosmetic items). Given the context of 
gender-based appeal in Korean MMOs such as BDO, there could also be a connection
between the number of female characters and a player's spending in the pearl shop.
The model therefore seeks to explore whether there 
really is a statistically significant connection between the total amount
of money spent in-game and the factors mentioned above. 
Equivalently,

@@

Equation \@ref(eq:linm) represents the model used in this paper, where
$Y$, the dependent variable, is a player's total spending in pearl shop,
$\beta_0$ is the intercept, $X_1$ is the covariate of total playtime,
$X_2$ is the covariate of the number of female characters the player has.
$X_3$ is the covariate of the player's rated importance of VP.
$X_4$ is the covariate of the player's rated importance of BK and OM.
$\beta_1 \beta_2, \beta_3, \beta_4$ are the coefficients of the variables.

@@

The Normal Q-Q plot (top-right) shows most points falling on the dashed line,
though there is also a considerable number of points that fall off the dashed line
on the right tail end, suggesting that the residuals may not be entirely normally
distributed.

@@

As shown in Table \@ref(tab:table1), some of the respondents had obtained the
free package for the game, which were frequently given out through various
methods by Pearl Abyss, as described in Section
\@ref(preliminary-analysis). Out of the 67 respondents
who obtained the free package of the game, 23 of them remained completely
free-to-play and did not spend any real world currency to purchase in-game
items nor other game packages.
The other 44 respondents--almost double those who remained completely
free-to-play--purchased in-game items on the pearl shop and/or other game
packages.

This is further elaborated upon in Table \@ref(tab:table3), which summarises
the dataset based on whether the respondent's spending status is considered
`completely free` if they obtained the free package for the game and did not
spent money on other game packages nor in the pearl shop, or `partially free`
if they obtained the free package for the game but spent money on other
game packges and/or in the pearl shop.
We can see from Table \@ref(tab:table3) that despite having a lower average
spending in both the pearl shop and game packages, the "partially free" players
still spent a substantial amount of money on further purchases for the game:
On average, for "partially free" respondents,
the amount of money spent on game package purchases accounts for only 6% of
their total spending on BDO. We observe a similar statistic for players who
did not obtain a free package for the game, whose spending on game packages
accounts for only 5% of their total spending on BDO.
In contrast, microtransactions in BDO account for roughly 95% of the total
revenue, as shown in table \@ref(tab:table4), a staggeringly high percentage.

@@

As discussed in Section \@ref(preliminary-analysis), Figure \@ref(fig:graph9) suggests
a difference in importance as regarded by the respondents. This is supported
by the statistics shown in Figure \@ref(fig:graph8), which show a stronger
positive linear correlation between rated importance of VP and spending on
VP when compared to the correlation between rated importance of BK and OM and
spending on BK and OM. On average, respondents spend $148.0288 USD on
purchasing VPs from the pearl shop, and spend $49.1202 USD on purchasing
BKs and OMs from the pearl shop.

Table \@ref(tab:table3) shows that on average, VP accounts for 11% of
a respondent's total spending on BDO (15% for partially free respondents).
BK and OM account for 4% of a respondent's total spending on BDO (5% for
partially free respondents).

@@

From a pure-revenue standpoint, there is a debate to be made about whether
or not a video game publisher
should charge an upfront cost on consumers for access to their game.
On one hand, giving concrete price tags to a game before its launch would grant
the publisher the ability to let consumers pre-order the game, injecting a
massive amount of funding into the company that could be used for future
developments and investments on other projects well before they even need to
finish and release the game.
On the other hand, price tags too high may discourage consumer interest in the
game, preventing them from ever engaging with the in-game cash shop which
is much better suited for long-term revenue generation.

@@

Another potential reason to this disinterest is the difference in price between
BK and OM, and VP: Without any discounts, 30 days of VP costs 1500 pearls
(roughly \$15.00 USD) while 30 days of BK/OM costs 2500 pearls (roughly \$25.00
USD), an increase in price by roughly 66%. There is no plausible explanation
as to why BK/OM are priced higher than VP except publisher bias; While most
players regard VP as the more important subscription item (as shown in Figure
\@ref(fig:graph9)), publishers of the game may simply think otherwise.
If possible, further extensions on this study should inquire the players about
their reasons for rating certain subscription items less important, be it the
price or its bonuses.

@@

Whales are often make up a major portion of a video game's revenue:
For example, according to Activision Blizzard's [@citeacti] 2021 fourth quarter
revenue release,
the company made a net revenue of \$8.086 billion USD, \$5.736 billion USD of
which is from in-game transactions and subscriptions. A surprisingly high 70.94%
of total revenue for the company is from sources other than upfront costs.

@@

As Table \@ref(tab:table4) shows, if we do not exclude the whales as outliers
from the dataset, then the average
revenue generated from the pearl shop accounts for roughly 95% 
This clearly demonstrates the importance of whales to a video game company's
profit, and why catering to these whales could often result in more profit
than focusing on satisfying the average consumer.

Whales are rare but their impact have not gone unnoticed. In fact, catering to 
whales is not a new
strategy for publishers by any means, as demonstrated by Jernström [@citepocket] 
, who is well versed in this type of monetisation and
has created a thorough guide for other publishers to follow suit. It is apparent
that publishers are already catching on to these whales and the best strategies
to appeal to them. This should state the significance of whales as the highest
potential source of income for a video game.
